An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-09-22 paper.tex
Tweak section title
Tidy (no content changes)

\title{An Empirical Analysis of the Internet Engineering Task Force 
       with Computational Methods}
\author{Colin Perkins \and
        Prashant Khare \and
        Mladen Karan \and
        Stephen McQuistin \and
        Waleed Iqbal \and
        Junaid Qadir \and
        Matthew Purver \and
        Patrick Healey \and
        Ignacio Castro \and
        Gareth Tyson}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/documents/rfcs_areas.pdf}
\caption{RFCs by area. \textit{Other} includes legacy RFCs, and RFCs from other non-IETF streams.}
\label{fig:rfcs_by_area}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/documents/unique_wgs_per_year_areas.pdf}
\caption{Number of publishing working groups. \textit{Other} includes legacy RFCs, IRTF research groups, and non-IETF streams.}
\label{fig:pub_wgs_yearly}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/documents/day_counts_yearly.pdf}
\caption{Days from first draft to RFC publication}
\label{fig:rfcs_days_to_pub}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/documents/draft_counts_yearly.pdf}
\caption{Number of drafts per RFC}
\label{fig:drafts_year}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/documents/page_counts_yearly_dt.pdf}
\caption{RFC page counts}
\label{fig:pages_year}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/documents/update_obsolete_yearly_pct.pdf}
\caption{RFCs that update or obsolete previous RFCs}
\label{fig:updates_year}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/documents/cite_counts_yearly.pdf}
\caption{Citations from RFCs to other Internet-Drafts and RFCs per RFC}
\label{fig:citations_year}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/documents/keyword_usage_rate.pdf}
\caption{Keyword occurrences per page}
\label{fig:keyword_usage_rates}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/tma-2023/errata-by-year.pdf}
\caption{Average errata filed per RFC for each year by RFC publication year,
grouped by IETF area (acronyms expanded in Table~\ref{tab:errata-stats-area}).}
\label{fig:errata_per_year}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/tma-2023/errata-submission-dates-area.pdf}
\caption{Days from RFC publication and errata filing by IETF area (acronyms
  expanded in Table~\ref{tab:errata-stats-area}).}
\label{fig:errata_submission_days}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/tma-2023/errata-by-status.pdf}
\caption{Errata filings by status, by publication year of the RFC.}
\label{fig:errata_status}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/tma-2023/errata-by-rfc-by-area.pdf}
\caption{CDF of errata filed per RFC by grouped by IETF area (acronyms
  expanded in Table~\ref{tab:errata-stats-area}).}
\label{fig:errata_per_rfc}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/tma-2023/location-percent.pdf}
\caption{Errata counts by percentile location in document (0 is the beginning; 100 is the end).}
\label{fig:errata_location_percent_count}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/tma-2023/section-title-counts.pdf}
\caption{Errata counts by section title for the more frequent section titles.}
\label{fig:errata_section_wise_counts}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/authors/top5_countries_normalised.pdf}
\caption{Authorship countries (normalised)}
\label{fig:author_countries_normalised}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/authors/continents_normalised.pdf}
\caption{Authorship continents (normalised)}
\label{fig:author_continents_normalised}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/authors/top5_affiliations_normalised.pdf}
\caption{Authorship affiliations (normalised)}
\label{fig:author_affiliations_normalised}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/authors/top5_affiliations_normalised_acad.pdf}
\caption{Academic affiliations (normalised)}
\label{fig:author_affiliations_normalised_acad}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/authors/repeat_authors.pdf}
\caption{Percentage of new authors per year.}
\label{fig:author_new}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/emails/pid_count_emailing_yearly.pdf}
\caption{Number of Person IDs exchanging emails each year}
\label{fig:pid_count_emailing_yearly}
\end{figure}

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/emails/frequency_emails_yearly_categories2.pdf}
\caption{Number of messages exchanged per year across different categories:
  messages mapped to the Datatracker (Datatracker Person-ID); messages by
  automated email addresses (Automated); messages by role-based addresses
  (Role-based); and messages not mapped to the Datatracker (New Person-ID)}
\label{fig:emailvol_by_year_catg}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/emails/yearly-draft-mention-volume.pdf}
\caption{Number of draft mentions in each year found in the mail lists}
\label{fig:draft_mentions}
\end{figure}

@@

\begin{itemize}
    \item \textit{Outgoing interaction}, where an RFC author responds to an
      email from other contributors (i.e., email sent).
    \item \textit{Incoming interaction}, where contributors respond to an
      email by the author (i.e., email received).
\end{itemize}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/emails/age_authors_RFCs.pdf}
\caption{Contribution duration distribution of authors of RFCs: junior-most
  author of each RFC, senior-most author of each RFC, and mean
  contribution-duration of all authors of each RFC}
\label{fig:age_dist_rfc_authors}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/emails/rfc_authors_degree.pdf}
\caption{CDF showing drift in annual degree (interaction with their
  network) of RFC authors over the period 2000-2020.}
\label{fig:degree_dist_rfc_authors}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/imc-2021/emails/junior_senior_authors_seniormem_indegree.pdf}
\caption{CDF showing number of senior contributors sending messages
  (in-degree) to junior and senior authors.}
\label{fig:junior_senior_indegree_seniormem}
\end{figure}

@@

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
% ICWSM 2022 paper Section 3
\subsubsection{The IETF as a Social Graph}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{figures-prev/icwsm-2022/degree_CDF.pdf}
\caption{Cumulative degree distribution of the email graph for different year-periods.}
\label{fig:degree_cdf}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{figures-prev/icwsm-2022/lcc_yearly_no_components.pdf}
\caption{Size of Largest Connected Component (LCC) and Number of Connected Components (NCC)}
\label{fig:lcc_size_yearly}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{figures-prev/icwsm-2022/lcc_proportion_granular_yearly.pdf}
\caption{Impact of removing participants by their influence on the size of the LCC.}
\label{fig:purge_nodes_largest_connected_component_number_components}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{figures-prev/icwsm-2022/lineplot_proportion_emailscount_top_percentile.pdf}
\caption{Proportion of emails sent (\%) by participants in each period 
(with 95\% confidence interval) according to their betweenness-centrality percentile (x-axis).
Y2-axis (purple) shows yearly count of emails.}
\label{fig:emailcount_top_percentile}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{figures-prev/icwsm-2022/lineplot_avg_areas_top_percentile.pdf}
\caption{Mean number of areas participated in (with 95\% confidence
  interval) according to their betweenness-centrality percentile in the
  x-axis, ranked from  top (0-10) to bottom percentile (91-100).}
\label{fig:areas_participation_top_percentile}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{figures-prev/icwsm-2022/lineplot_age_top_percentile.pdf}
\caption{Mean participation duration (with 95\% confidence interval)
  according to their betweenness-centrality percentile in the x-axis,
  ranked from  top (0-10) to bottom percentile (91-100).}
\label{fig:age_top_percentile}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{figures-prev/icwsm-2022/heatmap_top10_percent_overlap.pdf}
\caption{Yearly overlap (\%) of top 10\% influencers.}
\label{fig:heatmap_top10_overlap}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{figures-prev/icwsm-2022/new_influencers_top10_age_longevityInTop10.pdf}
\caption{Percentage of new influential participants breaking into top 10\%
  influencers (black); the average years of participation before entering
  top 10\% (purple); and minimum \#  years new influencers remain in top
  10\% (with 95\% confidence intervals).}
\label{fig:rate_new_influential_participants}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/icwsm-2022/topic-div.png}
\caption{Mean topic entropy (with 95\% confidence interval) according to
  their betweenness-centrality percentile in the x-axis, ranked from  top
  (0-10) to bottom percentile (91-100).}
\label{fig:topic_diversity}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/icwsm-2022/documents_proportion_published_top_percentile.pdf}
\caption{Average drafts authored (with 95\% confidence interval) according
  to their betweenness-centrality percentile in the x-axis, ranked from
  top (0-10) to bottom percentile (91-100).  Right-y axis (purple) shows
  yearly drafts per year.}
\label{fig:drafts_initiation_top_percentile}
\end{figure}

@@

\bottomrule
\end{tabular}
\caption{Overlap in the co-author and email graph.}
\label{tbl:correlation_sprmn}
\end{table}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/icwsm-2022/coauthor_affiliation_network/lineplot_non_overlapping_authors_emailnetwork_percentile.pdf}
\caption{Percentage of Top 20\% authors that are not 20\% influencers
  according to their betweenness-centrality (email graph) percentile in the
  x-axis, ranked from  top (0-10) to bottom percentile (91-100).}
\label{fig:non_overlapping_coauthornetwork_authors_emailnetwork}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.45\textwidth]{figures-prev/icwsm-2022/WG_chair_percentile_CDF_before_after.pdf}
 \caption{CDF of the percentile of betweenness-centrality of WG chairs in
  the email and co-authorship graph, one year before and after becoming
  chairs.}
\label{fig:wg_chair_before_after}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{figures-prev/icwsm-2022/coauthor_affiliation_network/2019_affiliations_in_otheryears_coauthor_network.pdf}
\caption{Authors in the most common affiliations of top 20\% authors
  (co-authorship graph) in 2015-2019.}
\label{fig:coauthor_affiliation_network2019_otheryears}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{figures-prev/icwsm-2022/coauthor_affiliation_network/heatmap_2019_top10_affiliation_collaboration.pdf}
\caption{Number of drafts co-authored by top 15 most frequently affiliated
  organisations. We only include the top 20\% authors (co-authorship graph)
  of 2015-2019.}
\label{fig:heatmap_2019_coauthordraft_most_frequent_org}
\end{figure}

>>>>

\title{An Empirical Analysis of the Internet Engineering Task Force 
       with Computational Methods}
\author{Mladen Karan \and
        Prashant Khare \and
        Waleed Iqbal \and
        Junaid Qadir \and
        Stephen McQuistin \and
        Patrick Healey \and
        Matthew Purver \and
        Ignacio Castro \and
        Gareth Tyson \and
        Colin Perkins}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/documents/rfcs_areas.pdf}
  \caption{
    RFCs by area. \textit{Other} includes legacy RFCs, and RFCs from other
    non-IETF streams.
  }
  \label{fig:rfcs_by_area}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/documents/unique_wgs_per_year_areas.pdf}
  \caption{
    Number of publishing working groups. \textit{Other} includes legacy
    RFCs, IRTF research groups, and non-IETF streams.
  }
  \label{fig:pub_wgs_yearly}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/documents/day_counts_yearly.pdf}
  \caption{
    Days from first draft to RFC publication
  }
  \label{fig:rfcs_days_to_pub}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/documents/draft_counts_yearly.pdf}
  \caption{
    Number of drafts per RFC
  }
  \label{fig:drafts_year}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/documents/page_counts_yearly_dt.pdf}
  \caption{
    RFC page counts
  }
  \label{fig:pages_year}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/documents/update_obsolete_yearly_pct.pdf}
  \caption{
    RFCs that update or obsolete previous RFCs
  }
  \label{fig:updates_year}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/documents/cite_counts_yearly.pdf}
  \caption{
    Citations from RFCs to other Internet-Drafts and RFCs per RFC
  }
  \label{fig:citations_year}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/documents/keyword_usage_rate.pdf}
  \caption{
    Keyword occurrences per page
  }
  \label{fig:keyword_usage_rates}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/tma-2023/errata-by-year.pdf}
  \caption{
    Average errata filed per RFC for each year by RFC publication year,
    grouped by IETF area (acronyms expanded in Table~\ref{tab:errata-stats-area}).
  }
  \label{fig:errata_per_year}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/tma-2023/errata-submission-dates-area.pdf}
  \caption{
    Days from RFC publication and errata filing by IETF area (acronyms
    expanded in Table~\ref{tab:errata-stats-area}).
  }
  \label{fig:errata_submission_days}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/tma-2023/errata-by-status.pdf}
  \caption{
    Errata filings by status, by publication year of the RFC.
  }
  \label{fig:errata_status}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/tma-2023/errata-by-rfc-by-area.pdf}
  \caption{
    CDF of errata filed per RFC by grouped by IETF area (acronyms expanded
    in Table~\ref{tab:errata-stats-area}).
  }
  \label{fig:errata_per_rfc}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/tma-2023/location-percent.pdf}
  \caption{
    Errata counts by percentile location in document (0 is the beginning;
    100 is the end).
  }
  \label{fig:errata_location_percent_count}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/tma-2023/section-title-counts.pdf}
  \caption{
    Errata counts by section title for the more frequent section titles.
  }
  \label{fig:errata_section_wise_counts}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/authors/top5_countries_normalised.pdf}
  \caption{
    Authorship countries (normalised)
  }
  \label{fig:author_countries_normalised}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/authors/continents_normalised.pdf}
  \caption{
    Authorship continents (normalised)
  }
  \label{fig:author_continents_normalised}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/authors/top5_affiliations_normalised.pdf}
  \caption{
    Authorship affiliations (normalised)
  }
  \label{fig:author_affiliations_normalised}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/authors/top5_affiliations_normalised_acad.pdf}
  \caption{
    Academic affiliations (normalised)
  }
  \label{fig:author_affiliations_normalised_acad}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/authors/repeat_authors.pdf}
  \caption{
    Percentage of new authors per year.
  }
  \label{fig:author_new}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/emails/pid_count_emailing_yearly.pdf}
  \caption{
    Number of Person IDs exchanging emails each year
  }
  \label{fig:pid_count_emailing_yearly}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/emails/frequency_emails_yearly_categories2.pdf}
  \caption{
    Number of messages exchanged per year across different categories:
    messages mapped to the Datatracker (Datatracker Person-ID); messages
    by automated email addresses (Automated); messages by role-based
    addresses (Role-based); and messages not mapped to the Datatracker
    (New Person-ID)
  }
  \label{fig:emailvol_by_year_catg}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/emails/yearly-draft-mention-volume.pdf}
  \caption{
    Number of draft mentions in each year found in the mail lists
  }
  \label{fig:draft_mentions}
\end{figure}

@@

\begin{itemize}
  \item \textit{Outgoing interaction}, where an RFC author responds
    to an email from other contributors (i.e., email sent).

  \item \textit{Incoming interaction}, where contributors respond to
    an email by the author (i.e., email received).
\end{itemize}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/emails/age_authors_RFCs.pdf}
  \caption{
    Contribution duration distribution of authors of RFCs:
    junior-most author of each RFC, senior-most author of
    each RFC, and mean contribution-duration of all authors
    of each RFC
  }
\label{fig:age_dist_rfc_authors}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/emails/rfc_authors_degree.pdf}
  \caption{
    CDF showing drift in annual degree (interaction with their network)
    of RFC authors over the period 2000-2020.
  }
  \label{fig:degree_dist_rfc_authors}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/imc-2021/emails/junior_senior_authors_seniormem_indegree.pdf}
  \caption{
    CDF showing number of senior contributors sending messages (in-degree)
    to junior and senior authors.
  }
  \label{fig:junior_senior_indegree_seniormem}
\end{figure}

@@

% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
% ICWSM 2022 paper Section 3
\subsubsection{Measuring Influence: The IETF as a Social Graph}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/degree_CDF.pdf}
  \caption{
    Cumulative degree distribution of the email graph for different
    year-periods.
  }
  \label{fig:degree_cdf}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/lcc_yearly_no_components.pdf}
  \caption{
    Size of Largest Connected Component (LCC) and Number of Connected
    Components (NCC)
  }
  \label{fig:lcc_size_yearly}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/lcc_proportion_granular_yearly.pdf}
  \caption{
    Impact of removing participants by their influence on the size
    of the LCC.
  }
  \label{fig:purge_nodes_largest_connected_component_number_components}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/lineplot_proportion_emailscount_top_percentile.pdf}
  \caption{
    Proportion of emails sent (\%) by participants in each period (with
    95\% confidence interval) according to their betweenness-centrality
    percentile (x-axis).  Y2-axis (purple) shows yearly count of emails.
  }
  \label{fig:emailcount_top_percentile}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/lineplot_avg_areas_top_percentile.pdf}
  \caption{
    Mean number of areas participated in (with 95\% confidence interval)
    according to their betweenness-centrality percentile in the x-axis,
    ranked from top (0-10) to bottom percentile (91-100).
  }
  \label{fig:areas_participation_top_percentile}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/lineplot_age_top_percentile.pdf}
  \caption{
    Mean participation duration (with 95\% confidence interval) according
    to their betweenness-centrality percentile in the x-axis, ranked from
    top (0-10) to bottom percentile (91-100).
  }
  \label{fig:age_top_percentile}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/heatmap_top10_percent_overlap.pdf}
  \caption{
    Yearly overlap (\%) of top 10\% influencers.
  }
  \label{fig:heatmap_top10_overlap}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/new_influencers_top10_age_longevityInTop10.pdf}
  \caption{
    Percentage of new influential participants breaking into top 10\%
    influencers (black); the average years of participation before entering
    top 10\% (purple); and minimum \#  years new influencers remain in top
    10\% (with 95\% confidence intervals).
  }
  \label{fig:rate_new_influential_participants}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/topic-div.png}
  \caption{
    Mean topic entropy (with 95\% confidence interval) according to their
    betweenness-centrality percentile in the x-axis, ranked from top (0-10)
    to bottom percentile (91-100).
  }
  \label{fig:topic_diversity}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/documents_proportion_published_top_percentile.pdf}
  \caption{
    Average drafts authored (with 95\% confidence interval) according to
    their betweenness-centrality percentile in the x-axis, ranked from top
    (0-10) to bottom percentile (91-100).  Right-y axis (purple) shows
    yearly drafts per year.
  }
  \label{fig:drafts_initiation_top_percentile}
\end{figure}

@@

    \bottomrule
  \end{tabular}
  \caption{
    Overlap in the co-author and email graph.
  }
  \label{tbl:correlation_sprmn}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/coauthor_affiliation_network/lineplot_non_overlapping_authors_emailnetwork_percentile.pdf}
  \caption{
    Percentage of Top 20\% authors that are not 20\% influencers according
    to their betweenness-centrality (email graph) percentile in the x-axis,
    ranked from  top (0-10) to bottom percentile (91-100).
  }
  \label{fig:non_overlapping_coauthornetwork_authors_emailnetwork}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/WG_chair_percentile_CDF_before_after.pdf}
  \caption{
    CDF of the percentile of betweenness-centrality of WG chairs in the
    email and co-authorship graph, one year before and after becoming
    chairs.
  }
  \label{fig:wg_chair_before_after}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/coauthor_affiliation_network/2019_affiliations_in_otheryears_coauthor_network.pdf}
  \caption{
    Authors in the most common affiliations of top 20\% authors
    (co-authorship graph) in 2015-2019.
  }
  \label{fig:coauthor_affiliation_network2019_otheryears}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{figures-prev/icwsm-2022/coauthor_affiliation_network/heatmap_2019_top10_affiliation_collaboration.pdf}
  \caption{
    Number of drafts co-authored by top 15 most frequently affiliated
    organisations. We only include the top 20\% authors (co-authorship
    graph) of 2015-2019.
  }
  \label{fig:heatmap_2019_coauthordraft_most_frequent_org}
\end{figure}
